### 2024-03-24 docs/projects/geography/chicago-bikes/index.qmd
Chicago bikes - rerendered

::: {.sourceClojure}
```clojure
(ns index
  (:require [tablecloth.api :as tc]
            [scicloj.noj.v1.vis.hanami :as hanami]
            [aerial.hanami.templates :as ht]
            [aerial.hanami.common :as hc]
            [clojure.string :as str]
            [tech.v3.dataset :as tmd]
            [tech.v3.datatype :as dtype]
            [tech.v3.datatype.functional :as fun]
            [fastmath-clustering.core :as clustering]
            [scicloj.kindly.v4.kind :as kind]
            [charred.api :as charred]))
```
:::

@@

<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>hours-0</th><th>map-0</th></tr></thead><tbody><tr><td>57</td><td>13013</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>0</td><td>12917</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>7</td><td>12853</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>27</td><td>12666</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>70</td><td>11639</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>

>>>>

# Chicago bikes - DRAFT

This page will be updated soon.

## Data sources:
- [Cyclistic bike share - Kaggle](https://www.kaggle.com/datasets/evangower/cyclistic-bike-share)
- [Cyclistic bike share - 2023 update - Kaggle](https://www.kaggle.com/datasets/godofoutcasts/cyclistic-bike-share-2023)
- [Chicago neighborhoods geojson by @blackmad](https://github.com/blackmad/neighborhoods/blob/master/chicago.geojson)

## Workflow

@@

<table class="table table-hover table-responsive"><thead><tr><th>cluster</th><th>n</th><th>hours-0</th><th>map-0</th></tr></thead><tbody><tr><td>15</td><td>13103</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/2.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/3.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>61</td><td>11728</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/4.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/5.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>29</td><td>11427</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/6.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/7.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>56</td><td>11393</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/8.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/9.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>36</td><td>11366</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/10.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/11.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>79</td><td>10406</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/12.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/13.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>21</td><td>10088</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/14.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/15.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>93</td><td>9943</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/16.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/17.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>76</td><td>9885</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/18.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/19.csv","format":{"type":"csv"}}});</script></div></td></tr><tr><td>19</td><td>9390</td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"encoding":{"y":{"field":"n","type":"quantitative"},"x":{"field":"hour","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"bar","tooltip":true},"width":400,"background":"floralwhite","height":300,"data":{"url":"index_files\/20.csv","format":{"type":"csv"}}});</script></div></td><td><div><script>vegaEmbed(document.currentScript.parentElement, {"usermeta":{"embedOptions":{"renderer":"svg"}},"width":400,"background":"floralwhite","title":{"text":"Chicago bike trips"},"layer":[{"data":{"url":"notebooks\/data\/chicago.geojson","format":{"type":"topojson"}},"mark":{"type":"geoshape","filled":false,"clip":true,"opacity":0.3}},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"},"longitude2":{"field":"end_lng","type":"quantitative"},"latitude2":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":"rule","width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"start_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"start_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"purple","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300},{"encoding":{"longitude":{"field":"end_lng","type":"quantitative"},"opacity":{"value":0.01},"latitude":{"field":"end_lat","type":"quantitative"}},"usermeta":{"embedOptions":{"renderer":"svg"}},"mark":{"type":"circle","color":"green","tooltip":true},"width":400,"background":"floralwhite","projection":{"type":"mercator"},"height":300}],"height":300,"data":{"url":"index_files\/21.csv","format":{"type":"csv"}}});</script></div></td></tr></tbody></table>
